An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Now using the spaghetti graph function to plot the CD results.

Figure~\ref{fig:CD_GDP_Lattice_Graph} compares predictions 
from the Cobb-Douglas models 
(with and without energy) to historical data.

**** Replace with a spaghetti graph? Countries in rows. Without energy and with energy in columns. ****

<<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
createCDLatticeGraph(energyType="Q")
@

>>>>

Figure~\ref{fig:CD_GDP_Spaghetti_Graph} compares predictions 
from the Cobb-Douglas models 
(with and without energy) to historical data.

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none")
cdQData <- loadCDSpaghettiGraphData(energyType="Q")
cdData <- rbind(cdData, cdQData)
cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy)
# createCDLatticeGraph(energyType="Q")
@
